---
output: github_document
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# kipettools : Tools for the KI PET Group

The kipettools package is a set of tools to help with regular tasks at the KI PET Centre involving interacting with outputs from the pipeline using R.  It mostly consists of convenience functions developed over the years which have been useful: due to this process, however, much of the code is not very pretty, coming from early stages of learning R, or from hacking something together for the job at hand.  Nevertheless, many of these tools have stood the test of time in being useful, so hopefully having them all documented and saved in one place will make them more so..


## Installation

The package can be installed in R directly from GitHub, using the *devtools* package as follows:

```{r, eval=F}
# install.packages("devtools")
devtools::install_github("mathesong/kipettools")
```



## Main functions

The primary functions available here are the following:

* *srtm2xlsx*: Create a BP Sheet from a set of srtmresults.txt files
* *kfresults\_getData*: Extract TACs and other information from a kinfitresults file
* *roistats\_getData*: Extract TACs and other information from a roistats file


## New Functions and Requirements

I am also busy implementing some functions for extracting information from and converting ecat7 files.  This includes some wrapper functions around terminal applications.  For these, you will need both gzip and the Turku PET Centre C libraries ([tpcclib](http://www.turkupetcentre.net/petanalysis/sw_pet.html#tpc)) installed and added to your path.  For Windows users, gzip is installed with [Rtools](https://cran.r-project.org/bin/windows/Rtools/) - alternatively, you can use installr::install.Rtools().
